### 2022-11-15 NSF2022/Description/specificaim1v2.tex
yny 1115b

\section{Proposed Research}
\label{sec:proposed-work}
This proposal is an outgrowth of the PIs' ongoing successful
collaboration. Building off complementary expertises, the specific aims
of this proposal are: mathematical analysis and three-dimensional
membrane energies (\S\ref{sec:specificaim1}: PI Ryham), BIE
implementation for large granule-number and three-dimensional
suspensions (\S\ref{sec:specificaim2}: PI Quaife), and kinetic theory
(\S\ref{sec:specificaim3}: PI Young).

@@

The second problem considers the approximation of elastic energy of
curves and surfaces, and seeks to make rigorous the simulation results
of~\cite{FuQuRyYo22, Fu2018_SIAM}. We employ the so-called
``amphiphilic'' boundary condition that leads a collection of
granules to form bilayers. Referring to
Figure~\ref{fig:amphiphilic_assembly}, 
\begin{align}
\label{eq:amphiphilic_BC}
  \phi(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
    (\xx - \aa_i)/c_i + 1\right), \quad \xx \in \Gamma_i,
\end{align}
where $\dd_i$ is the unit length director, $\aa_i$ is the center, and
$c_i$ the ``radius'' of the $i$th granule. The phase $\phi$ takes values
close to $1$ in the direction $\dd_i$, representing a hydrophobic tail,
and values close to $0$ in the direction $\dd_i$ representing the
hydrophilic head.

>>>>

\section{Proposed Research}
\label{sec:proposed-work}
This proposal is an outgrowth of the PIs' ongoing successful
collaboration. Building off complementary expertises, the specific aims
of this proposal are: mathematical analysis and three-dimensional
membrane energies (\S\ref{sec:specificaim1}: PI Ryham), BIE
implementation for large granule-number and three-dimensional
suspensions (\S\ref{sec:specificaim2}: PI Quaife), and kinetic theory modeling
(\S\ref{sec:specificaim3}: PI Young).

@@

The second problem considers the approximation of elastic energy of
curves and surfaces, and seeks to make rigorous the simulation results
of~\cite{FuQuRyYo22, Fu2018_SIAM}. We employ the so-called
``amphiphilic'' boundary condition that leads a collection of
granules to form bilayers. Referring to
Figure~\ref{fig:amphiphilic_assembly}, 
\begin{align}
\label{eq:amphiphilic_BC}
  \phi(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
    (\xx - \aa_i)/c_i + 1\right), \quad \xx \in \Gamma_i,
\end{align}
where $\dd_i$ is the director, $|\dd_i| = 1$, $\aa_i$ is the center, and
$c_i$ the ``radius'' of the $i$th granule. The phase $\phi$ takes values
close to $1$ in the direction $\dd_i$, representing a hydrophobic tail,
and values close to $0$ in the direction $\dd_i$ representing the
hydrophilic head.
